Artin Group Presentations Arising from Cluster Algebras

### 2014-07-21 Paper.tex
improved section 6 and small changes

\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{matrix, calc, arrows}
\usepackage{latexsym,amscd,epsfig,verbatim}
\usepackage[margin=1in,letterpaper,portrait]{geometry}

@@

%\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{note}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
\newcommand\fri{s_4^{-1}}
\newcommand\fr{s_4}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}
\newcommand\V{V(\Gamma)}

@@

\begin{cor}
\label{local_three_picture}
Let $\Gamma$ be the a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$

@@

In this section we prove our main result:

\begin{thm}\label{thm:main}
Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.  Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$\todo{we should pick notation for this}.
\end{thm}

Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  To help us define an isomorphism from $A_{\Gamma}$ to $A_{\Gamma^{\prime}}$ we define an element $t_i\in A_{\Gamma}$ for each vertex $i\in \Gamma$ by

\begin{displaymath}
t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \Gamma\\
				s_i & \mbox{otherwise}\\
	\end{cases}
\end{displaymath}

In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main}.

\begin{prop}\label{prop:ti_relations}
The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
\end{prop}
\todo{This propositions seems to be worded confusingly. I see this is what they say in Barot and Marsh, but I still find it confusing. Maybe it's clearer to say that if we take $p_i$ to be the generators of $\Gamma',$ and they satisfy a relation $r(p_1,\ldots, p_{|\Gamma|}) = e,$ if and only if $t_i$ satisfy the same relation $r(t_1,\ldots, t_{|\Gamma|}) = e.$}
\todo{Maybe it would make more sense to break this up into 2 lemmas, like Barot and Marsh do}

\begin{proof}[Proof of Theorem \ref{thm:main}]
Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$. \todo{Weren't the $t_i$ defined in terms of the $s_i$ for $A(\Gamma)$? It seems like there are two different $s_i,$ one for $\Gamma$ and one for $\Gamma'$ and this is confusing me.}  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.  Define a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
\todo{It seems like there is an abuse of notation here. You have defined $\phi:A(\Gamma') \rightarrow A(\Gamma),$ but it looks like it is mapping $A(\Gamma^{op} \rightarrow A((\Gamma^{op})')$ here. Please make clearer what this map $\phi$ is.}
Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.  Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.  Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
\todo{I think you have the right idea, but I don't understand how you always have elements in $A(\Gamma)$ and never elements in $A(\Gamma').$ I think the problem lies in the definition of $\phi.$}
Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.  In each of these cases we have that

$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(s_i^{-1})) = \Delta(s_i^{-1}) = s_i$$

@@

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
First we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when $i=k$ or $j=k$.  Without loss of generality suppose that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$. \todo{Isn't there also the case of an arrow from k to j? Obviously it's symmetric, but isn't it worth saying?}  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.  Suppose $m_{ij} = 3$.  Then $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, and we have

@@

\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore

$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$

\todo{An extra step inserting and removing inverses here would be helpful.}

\noindent If $m_{ij} = 6$, then $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$, so

$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
\todo{An extra step inserting and removing inverses here would be helpful, as above}

\todo{Instead of saying If mij = 3, try \vskip.1in
\noindent
{\sf The case $m_{ij} = 3$}}

Next we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when at most one of $i$ and $j$ is connected to $k$.  The only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.  Without loss of generality, suppose there is an arrow $i\rightarrow k$.  Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.  Suppose $m_{ij} = 2$. \todo{It seems like the previous two sentences should be switched? Again try using cases to break it up more clearly for the reader, as I mentioned in a previous todo.} Then $s_is_j = s_js_i$, so we have that

$$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
\todo{It looks like you're also using here that $s_j$ commutes with $s_k^{-1}.$ I agree it's obvious, but maybe it's worth spelling out}

\noindent If $m_{ij} = 3$, then $s_is_js_i = s_js_is_j$, so we have that

@@

\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so we have that

$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_js_is_js_i$$

\noindent Finally if $m_{ij} = 6$, then $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that

@@

The remaining $(R2)'$ relations that need to be check are the relations for $t_i$ and $t_j$ when both $i$ and $j$ are connected to $k$.  The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in \todo{where are they enumerated?}.  We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.  We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).

\begin{enumerate}[a)]
\item
\begin{enumerate}[i)]
\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
t_it_jt_i &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}\\
&= s_ks_is_js_ks_j^{-1}s_is_k^{-1}\\
&= s_ks_js_is_ks_is_j^{-1}s_k^{-1}\\
&= s_ks_js_ks_is_ks_j^{-1}s_k^{-1}\\
&= s_js_ks_js_is_j^{-1}s_k^{-1}s_j\\
&= s_js_ks_is_k^{-1}s_j\\
&= t_it_jt_i
\end{align*}

\begin{align*}
t_jt_k^{-1}t_it_k &= s_js_k^{-1}s_ks_is_k^{-1}s_k\\
&= s_js_i\\
&= s_is_j\\
&= t_k^{-1}t_it_kt_j\\
\end{align*}

\item $$t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}s_js_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}s_ks_js_ks_is_ks_i^{-1}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_js_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}\\
&= e
\end{align*}

We also have
$$t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$$

\item
\begin{align*}
t_it_j &= s_is_ks_js_k^{-1}\\
&= s_is_j^{-1}s_ks_j\\
&= s_j^{-1}s_ks_js_i\\
&= s_ks_js_k^{-1}s_i\\
&= t_jt_i
\end{align*}
\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
&= s_i^{-1}s_ks_is_js_i^{-1}s_ks_is_js_i^{-1}s_k^{-1}s_is_j^{-1}s_i^{-1}s_k^{-1}s_is_j^{-1}\\
&= s_i^{-1}s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}s_i\\
&= e
\end{align*}
We also have
$$ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$$

\item
\begin{align*}
s_k^{-1}t_it_jt_i^{-1}t_j^{-1}s_k &= s_k^{-1}s_is_ks_js_k^{-1}s_i^{-1}s_ks_j^{-1}\\
&= s_is_ks_i^{-1}s_js_is_k^{-1}s_i^{-1}s_j^{-1}\\
&= e
\end{align*}

\end{enumerate}
\item
\begin{enumerate}[i)]
\item
\begin{align*}
s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1} &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
&= e
\end{align*}

\begin{align*}
t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
&= e\\
\end{align*}

\item This follows from part (i) by symmetry
\end{enumerate}
\end{enumerate}

Next we check that the $t_i$ satisfy the (R3) relations defined by the chordless cycles in $\Gamma'$.  We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.  By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.  Note that we have already checked cases (a)-(d) above, so we only need to check cases (e)-(l).

\begin{enumerate}[a)]
\setcounter{enumi}{4}
\item
Without loss of generality we label the vertices as follows:\todo{insert diagrams}

@@

\item
\begin{align*}
t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= e\\
\end{align*}

>>>>

\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{matrix, calc, arrows}
\usepackage{latexsym,amscd,epsfig,verbatim}
%\usepackage[margin=1in,letterpaper,portrait]{geometry}

@@

%\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{note}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
%\newcommand\fri{s_4^{-1}}
%\newcommand\fr{s_4}
%\newcommand\tri{s_3^{-1}}
%\newcommand\tr{s_3}
%\newcommand\twi{s_2^{-1}}
%\newcommand\tw{s_2}
%\newcommand\oni{s_1^{-1}}
%\newcommand\on{s_1}
\newcommand\V{V(\Gamma)}

@@

\begin{cor}
\label{local_three_picture}
Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$

@@

\noindent In this section we prove our main result:

\begin{thm}\label{thm:main}
Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.  Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$
\end{thm}

Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively.  We will also abuse notation and write $u_i$ for the generators of $A_{\left(\Gamma^{op}\right)^\prime}$ as well, making use of the fact that $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.

In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main} and then split into Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.

\begin{prop}\label{prop:ti_relations}
The map $\varphi \colon A_{\Gamma^\prime}\rightarrow A_{\Gamma}$ defined by
\begin{displaymath}
\varphi(r_i) = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \Gamma\\
				s_i & \mbox{otherwise}\\
	\end{cases}
\end{displaymath}

\noindent is a group homomorphism.
\end{prop}

\todo{do we define $m_{ij}'$ somewhere?}

\begin{proof}[Proof of Theorem \ref{thm:main}]
By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism.  We also abuse notation and write $\varphi\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ by letting $\varphi(q_i)$ equal $u_ku_iu_k^{-1}$ if there is an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^\prime$, and $u_i$ otherwise, and this is a homomorphism by Proposition \ref{prop:ti_relations} as well.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta$ that sends $s_i\in A(\Gamma)$ to $q_i^{-1}\in A(\Gamma^{op})$ and $u_i\in A_{\left(\Gamma^\prime\right)^{op}}$ to $r_i\in A_{\Gamma^\prime}$ is well-defined.  We then have a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$

Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.  Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that

$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(q_k^{-1}q_i^{-1}q_k)) = \Delta(u_i^{-1}) = r_i$$

Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.  In each of these cases we have that

$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(q_i^{-1})) = \Delta(u_i^{-1}) = r_i$$

@@

We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.  Proofs that the $t_i$ satisfy these relations are divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.  Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.

\begin{lem}\label{lem:r2a_relations}
Let $i,j$ be distinct vertices of $\Gamma$.
\begin{enumerate}[(a)]
\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^k = e$.
\item If at most of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^k = e$.
\end{enumerate}
\end{lem}

\begin{proof}
For case $(a)$, suppose without loss of generality that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.
Here we have $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, so

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here we have $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore

$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here we have $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.  As in the previous case, we add an remove pairs $s_is_i^{-1}$ as necessary, giving

$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$

For case $(b)$, the only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.  Without loss of generality, suppose there is an arrow $i\rightarrow k$.  Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.

\vskip.1in
\noindent
{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so we have that

$$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.  Here $s_is_js_i = s_js_is_j$, so we have that

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here $s_is_js_is_j = s_js_is_js_i$, so we have that

$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = t_jt_it_jt_i$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that

@@

\end{proof}

\begin{lem}\label{lem:r2b_relations}
Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^k = e$.
\end{lem}

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.  We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).  Within each case we view the subdiagram on the left as a subdiagram of $\Gamma$ in the subcase $(i)$ and as a subdiagram of $\Gamma^\prime$ in the subcase $(ii)$.\todo{Disaster.  Open to suggestions for how to make this more clear}

Throughout the proof we will make frequent use of the fact that if $m$ and $n$ are vertices of $\Gamma$, then

$$s_ms_ns_m = s_ns_ms_n \Leftrightarrow s_ms_ns_m^{-1} = s_n^{-1}s_ms_n \Leftrightarrow s_ms_n^{-1}s_m^{-1} = s_n^{-1}s_m^{-1}s_n \Leftrightarrow s_m^{-1}s_n^{-1}s_m^{-1} = s_n^{-1}s_m^{-1}s_n^{-1}$$

When helpful, we underline the sections of an expression that are about to be manipulated.  We also frequently combine two applications of $A_{\Gamma}$ relations when one manipulation is simply commuting pairs of variables.

\begin{enumerate}[a)]
\item
\begin{enumerate}[i)]
\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$.
\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$.
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
t_it_jt_i &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
&= s_k\underline{s_is_j}s_k\underline{s_j^{-1}s_i}s_k^{-1}\\
&= s_ks_j\underline{s_is_ks_i}s_j^{-1}s_k^{-1}\\
&= \underline{s_ks_js_k}s_i\underline{s_ks_j^{-1}s_k^{-1}}\\
&= s_js_k\underline{s_js_is_j^{-1}}s_k^{-1}s_j\\
&= s_js_ks_is_k^{-1}s_j\\
&= t_it_jt_i
\end{align*}

\item We have $t_it_j = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = t_jt_i$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$
\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}\underline{s_js_ks_is_j}s_k\underline{s_j^{-1}s_i^{-1}s_j}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_k\underline{s_is_k^{-1}s_ks_j}s_ks_is_ks_i^{-1}s_k^{-1}\underline{s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}}\\
&=s_ks_j\underline{s_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}}s_j^{-1}s_k^{-1}\\
&= e
\end{align*}

\item We have $t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= \underline{s_ks_is_k^{-1}}s_j\underline{s_ks_is_k^{-1}}s_j\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\\
&= s_i^{-1}s_k\underline{s_is_js_i^{-1}}s_k\underline{s_is_js_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}s_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}}\\
&= s_i^{-1}\underline{s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}}s_i\\
&= e
\end{align*}

\item Since $s_js_k^{-1}s_is_k = s_k^{-1}s_is_ks_j$, we have that $s_js_k^{-1}s_i^{-1}s_k = s_k^{-1}s_i^{-1}s_ks_j$, hence

$$t_it_jt_i^{-1}t_j^{-1} = s_is_k\underline{s_js_k^{-1}s_i^{-1}s_k}s_j^{-1}s_k^{-1} = s_is_ks_k^{-1}s_i^{-1}s_ks_js_j^{-1}s_k^{-1} = e$$

\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have that \todo{refer to lemma}
\begin{align*}
s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
&= e
\end{align*}

\item This follows from part (i) by symmetry
\end{enumerate}
\end{enumerate}
\end{proof}

\begin{lem}\label{lem:r3_relations}
The elements $t_i$ satisfy the $(R3^\prime)$ relations in $\Gamma^\prime$.
\end{lem}

\begin{proof}
We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.  By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.

\begin{enumerate}[a)]
\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_k^{-1}t_it_kt_j$

\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$

\item We have $ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$

\item We have that
\begin{align*}
t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
&= e\\
\end{align*}

\item
Without loss of generality we label the vertices as follows:\todo{insert diagrams}

@@

\item
\begin{align*}
& t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= e\\
\end{align*}
